---
title: "Ggplot2 and dplyr review for exam"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Main Idea

- I am providing this to help you review for the exam.

# Notes

First, load the `tidyverse`,`viridis`, and `fivethirtyeight` packages.

```{r packages, warning = FALSE, message = FALSE}
library(tidyverse)
library(viridis)
library(fivethirtyeight)
```

## Endorsements Data

I am naming an object here so that we can look at the data in the viewer. This data is about presidential primary endorsements from 1980 to 2012.

```{r load-data, message=FALSE}
endorsements <- endorsements
```

### Some ggplot-specific practice

#### Numeric Variables

Please make a histogram for the number of endorsement points. Remember to include informative labels.

```{r histogram}

```

### Categorical Variables

Please make a bar plot of the number of candidates by party in the dataset and include informative labels.

```{r bar-plot}

```

**Segmented bar plots** can be used to visualize two categorical variables. Let's say you were interested in how many candidates ran for each party by year. 

Now please make a segmented bar plot using `viridis` colors for the number of candidates who ran in each party by year.

```{r segmented-bar-plot}

```

## Dplyr and ggplot practice problems

1) Please make a bar plot of the number of **Democratic** candidates by year.

```{r combine, warning=FALSE}

```

2) How many candidates raise a lot of money, a medium amount of money, and a small amount of money. Make a segmented barplot showing the number of candidates in each party who raise 1) under 1 million, 2) between 1 and 2 million, and 3) above 2 million. You will need to use a dplyr command first before making the plot. Hint: the command `case_when` might be useful here. [This page](https://www.sharpsightlabs.com/blog/case-when-r/) may be useful here.

```{r combine-2, warning=FALSE}

```

**Remember that you put the pipeline operator between the lines for dplyr and a + between lines for ggplot.**

### Additional Resources

### GGplot2
- https://ggplot2.tidyverse.org/
- https://raw.githubusercontent.com/rstudio/cheatsheets/master/data-visualization-2.1.pdf
- http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html
- https://medium.com/bbc-visual-and-data-journalism/how-the-bbc-visual-and-data-journalism-team-works-with-graphics-in-r-ed0b35693535
- https://ggplot2-book.org/
- https://ggplot2.tidyverse.org/reference/geom_histogram.html
- https://rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf
- https://github.com/GraphicsPrinciples/CheatSheet/blob/master/NVSCheatSheet.pdf

## Dplyr

- https://rstudio.com/wp-content/uploads/2015/02/data-wrangling-cheatsheet.pdf
- https://style.tidyverse.org/